\ldots

### 2013-06-13 summer13/frac2.tex
added alternatives

>>>>

\subsection{Alternatives}

If this formulation of trace does not work, we have a few alternatives:

\item Don't bother choosing a default element at all. We did this previously
with the relational semantics, without much success, but perhaps there's a
better way of looking at it.

\item Choose a canonical representative of the type {{b}} that's being traced
out. This seems like it's a strictly worse option than parameterizing it, but
it's still on the table, at least for now.

\item Focus on the combinator. Jacques pointed out that our old version of trace
``worked'' whenever the part of {{c}} acting on {{b}} was equivalent to the
identity. This seems promising, but I'm not quite sure how to think about it
yet, so I'm ignoring it for now. It's definitely something we want to look at,
though, especialy if the current approach doesn't work.
